---
title: "Day 1 mini-project"
author: "Suzana Iacob & Asher Wright"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r}

# INSTRUCTIONS

# You are a seasoned data scientist who has just arrived in Boston. You're looking to go see the sights, but you don't know where they are! Instead of buying a tourist guide like a Muggle, you are going to use your skills in exploratory data analysis and visualization to identify some of the cool spots to visit. 

# Working with your partner, conduct analyses to identify at least THREE cool spots that you want to check out. Use the dashboard format to communicate your findings. You can check e.g. on Google to confirm your findings, but you should include clear commentary indicating how your analysis supports your findings. I've included some of the code from the script we worked on together to help you get started. 

```

```{r}
# You may find the following resources useful: 
# - Your team member(s)! 
# - Data wrangling [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf), 
# - `R` graphics [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf), 
# - [`R` Graphics Cookbook](http://www.cookbook-r.com/Graphs/)
# - [RMarkdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
```

```{r data_prep}
# put your data preparation code here. To get you started, the data preparation we performed in the session previously has already been pasted in. Feel free to add any additional data preparation code needed for your visualizations

listings <- read_csv('../../data/listings.csv')
calendar <- read_csv('../../data/calendar.csv')

source("clean_prices.R")
listings <- clean_prices(listings)
calendar <- clean_prices(calendar)
```

# Top 3 Sunniest AirBnb Spots in Boston Area

Column {data-width=650}
-----------------------------------------------------------------------

### A map of the sunny spots in the area! 

```{r box_1}
library(ggmap)
sunny_listings <- listings %>%
  mutate(is_sunny = (grepl('sunny', summary))) %>%
  filter(is_sunny)

# boston_coords <- c(left = -71.151, bottom = 42.3901, right = -71.0189, top = 42.3901)

boston_coords <- c(left   = -71.1510, 
				   bottom = 42.3201, 
				   right  = -71.0189, 
				   top    = 42.3701)

basemap <- get_map(location = boston_coords)

# The ggmap with basemap is just the same as any other ggplot object, with pre-built aesthetics: lon on the x axis and lat on the y axis. Let's make a plot of all the listings in our data set:

ggmap(basemap) +
  geom_point(aes(x = longitude, y = latitude, color=neighbourhood), data = sunny_listings, size = 1)
```

Column {data-width=350}
-----------------------------------------------------------------------
### Sunny Neighbourhoods! 

Check out the most sunny neighbourhoods in the Boston Area! We explored which AirBnb spots were sunny. You'll see those on the (cut-off) map to the left! Notice the different clumps in different neighbourhoods.

```{r box_3}
# Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 

neighbourhood_count <- sunny_listings %>%
  group_by(neighbourhood) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

# head(neighbourhood_count)
library(knitr)
kable(head(neighbourhood_count, 10), caption = 'Sunny Neighbourhoods')
```
We recommend going to Alliston-Brighton, Dorchester, and Jamaica Plain! You should only go to the sunniest places possible. Check out some AirBnB listings there.

